A pair of co-moving, Sun-like stars with different chemical abundances:\\ a possible signature of copious rocky accretion (needs work)

### 2017-04-16 paper/ms.tex
tweak

% to-do list
% ----------
% - add items here
% style notes
% -----------
% - This file generates by Makefile; don't be typing ``pdflatex'' or some bullshit.
% - Line break between sentences to make the git diffs readable.
% - Use \, as a multiply operator.
% - Reserve () for function arguments; use [] or {} for outer shit.
% - Use \sectionname not Section, \figname not Figure, \documentname not Article or Paper or paper.

@@

\begin{abstract}
  We report and discuss the discovery of a co-moving pair of bright stars,
  HD 240429 and HD 240430, with their detailed abundances measured.
  The kinematics of the two stars from Gaia proper motions and spectroscopic RVs
  are completely consistent with them co-moving in space.
  Yet, the metallicities and the abundances of XX elements between the stars
  separated by $\sim 0.6$~pc in space are very different,
  challenging the simple picture that these co-moving pairs are once wide binaries
  formed in a coeval star-forming event but now tidally stripping.
  We consider such and such scenarios of the formation of such pairs.
\end{abstract}

>>>>

% to-do list
% ----------
% - Add references and uncertainties to Table 1

% style notes
% -----------
% - This file generates by Makefile; don't be typing ``pdflatex'' or some bullshit.
% - Line break between sentences to make the git diffs readable.
% - Use \, as a multiply operator.
% - Reserve () for function arguments; use [] or {} for outer shit.
% - Use \sectionname not Section, \figname not Figure, \documentname not Article or Paper or paper.

@@

\begin{abstract}
  We report and discuss the discovery of a co-moving pair of bright solar-type
  stars, HD 240429 and HD 240430, with significant differences in their chemical
  abundance patterns.
  The two stars are co-spatial ($|\Delta \bs{x}| < XX~\pc$) at a distance of
  $r\approx 100~\pc$ with nearly identical three-dimensional velocities
  ($|\Delta \bs{v}| < XX~\kms$ with 95\% confidence), as inferred from \gaia\
  \tgas\ proper motions and high resolution radial velocity measurements.
  Both stars are young with ages $\approx$$500~{\rm Myr}$ as estimated from
  their lithium abundances, favoring the idea that they were born together and
  are or were recently a bound, wide binary system.
  However, the metallicities and chemical abundances of refractory
  elements of the two stars are very different, challenging this simple picture.
  In order to reconcile the seemingly contradictory observations,
  we consider scenarios in which the pair is unrelated despite
  its current spatial and kinematic configuration, and
  those in which the pair formed together but may now have different chemistry.
  In the latter, we consider the possibility that the more metal-rich of the two,
  HD 240430, accreted $\approx$10's of Earth masses of protoplanetary, rocky material,
  selectively enhancing the refractory elements.
  Direct-imaging and precision radial velocity follow-up to study the existence
  or properties of planetary systems around these stars would help distinguish
  these scenarios.
\end{abstract}
